Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants\thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN 712689 SC$^2$.}

### 2017-05-05 cav2017/cav2017.tex
minor typo

A discrete-time LTI system as \eqref{eq:closedloopss} is asymptotically
stable if all the roots of its characteristic polynomial (i.e., the
eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
circle of the complex plane, i.e., if their absolute values are strictly less than
one~\cite{astrom1997computer} (this simple sufficient condition can be generalised, 
however this is not necessary in our work).  
In this paper, we express this stability specification $\phi_\mathit{stability}$ in terms of a check known as
\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic formula to
select the entries of matrix $K$ so that the closed-loop dynamics are shaped
as desired.

>>>>

A discrete-time LTI system as \eqref{eq:closedloopss} is asymptotically
stable if all the roots of its characteristic polynomial (i.e., the
eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
circle of the complex plane, i.e., their absolute values are strictly less than
one~\cite{astrom1997computer} (this simple sufficient condition can be generalised, 
however this is not necessary in our work).  
In this paper, we express this stability specification $\phi_\mathit{stability}$ in terms of a check known as
\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic formula to
select the entries of matrix $K$ so that the closed-loop dynamics are shaped
as desired.
